---
title: "Creating Model for Training Data"
author: Angela Zhao
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE,dpi=500}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)
library(here)
library(cvTools)
library(coefplot)
library(glmnet)
library(GGally)
library(ROCR)

file_raw_train_data <-
  here("data/train_data_speed_dating.csv")

recode_race <-
  c(
    "1" = "Black", 
    "2" = "White", 
    "3" = "Hispanic", 
    "4" = "API", 
    "5" = "Indigenous",
    "6" = "Other"
  )
  

recode_goal <-
  c(
    "1" = 'Seemed like a fun night out',   
    "2" = "To meet new people",
    "3" = "To get a date", 
    "4" = "Looking for a serious relationship",
    "5" = "To say I did it",
    "6" = "Other"
  )


recode_date <- c(
  "1" = 'Several times a week',   
  "2" = "Twice a week",
  "3" = "Once a week", 
  "4" = "Twice a month",
  "5" = "Once a month",
  "6" = "Several times a year",
  "7" = "Almost never"
)


recode_go_out <-
  c(
    "1" = 'Several times a week',   
    "2" = "Twice a week",
    "3" = "Once a week", 
    "4" = "Twice a month",
    "5" = "Once a month",
    "6" = "Several times a year",
    "7" = "Almost never"
    
  )

```

## Reading and cleaning Data


```{r}
train <-
  file_raw_train_data %>% 
  read_csv()


# Added in the ratings of partner rating you and you rating the partner
# diff is the avg of partner rating you - avg of you rating the partner

train <-
  train %>% 
  mutate_at(
    vars(
      career_c, 
      field_cd,
      race,
      race_o,
      zipcode,
      go_out,
      date,
      goal,
      met,
      met_o,
      samerace,
      gender,
      match
    ), 
    as.character
  ) %>% 
  mutate(
    field_cd = 
      case_when(
        field_cd %in% c("2", "4", "5", "10") ~ "STEM", 
        field_cd %in% c("1", "3", "8", "9", "11", "13") ~ "Social_Science",
        field_cd %in% c("6", "7", "14", "15", "16", "17") ~ "Humanities",
        TRUE ~ "Other"
      ), 
    race = recode(race, !!! recode_race), 
    goal = recode(goal, !!! recode_goal),
    met = if_else(met == "2", "0", met), 
    met_o = if_else(met_o == "2", "0", met_o),
    race_o = recode(race_o, !!! recode_race), 
    gender = if_else(gender == "0", "female", "male"),
    career_c = 
      case_when(
        career_c %in% c("3", "4", "5") ~ "STEM", 
        career_c %in% c("1", "7", "8", "9", "10", "11", "12", "13", "17") ~ "Social_Science",
        career_c %in% c("6") ~ "Humanities",
        TRUE ~ "Other"
      )
  ) %>%
  mutate_at(
    vars(
      career_c,
      field_cd,
      race,
      race_o,
      goal,
      met,
      met_o,
      gender
    ),
    as.factor
  )
```

## Normalize the preferences, if out of 100, to percentages instead. 

```{r}

train <-
  train %>% 
  rowwise() %>% 
  mutate(
    sum_2_1 = sum(c(attr2_1, sinc2_1, intel2_1, fun2_1, amb2_1, shar2_1)), 
    sum_4_1 = sum(c(attr4_1, sinc4_1, intel4_1, fun4_1, amb4_1, shar4_1)),
  ) %>%
  mutate_at(
    vars(attr2_1, sinc2_1, intel2_1, fun2_1, amb2_1, shar2_1), 
    ~ . / sum_2_1
  ) %>%
  mutate_at(
    vars(attr4_1, sinc4_1, intel4_1, fun4_1, amb4_1, shar4_1), 
    ~ . / sum_4_1
  ) %>%
  dplyr::select(-c(sum_2_1, sum_4_1))

train <-
  train %>% 
  rowwise() %>% 
  mutate(
    rating = sum(c(attr, sinc, intel, fun, amb, shar)), 
    avg_partner_rating = 
      mean(c(attr, sinc, intel, fun, amb, shar), na.rm = TRUE) / 10
  ) %>%
  mutate_at(
    vars(attr, sinc, intel, fun, amb, shar), 
    ~ . / rating
  ) %>% 
  select(-rating)

```


## Choosing Variables

```{r}
# Selecting only the variables that determine perception of the round of speed

# Field and career are too unevenly entered, so best to use the coded versions instead. 

vars_wanted <-
  train %>% 
  select(
    rowname, 
    gender, 
    condtn, 
    match:race_o,
    like_o:age, 
    field_cd, 
    race:imprelig, 
    goal:go_out, 
    career_c:exphappy, 
    dec:met, 
    avg_partner_rating
  ) %>%
  select(-c(met, met_o, dec)) %>% 
  summarize_all(~ sum(is.na(.))) %>% 
  summarize_all(~ sum(.)) %>% 
  mutate_all(~ . / 4258) %>% 
  pivot_longer(
    cols = everything(), 
    names_to = "var", 
    values_to = "percent_missing"
  ) %>% 
  filter(percent_missing < 0.5) 

vars_wanted <-
  vars_wanted %>% 
  arrange(desc(percent_missing)) %>% 
  filter(var != "income") %>% 
  pull(var)

all_training_data <-
  train %>% 
  select(rowname, all_of(vars_wanted))


```

## Rescaling 1-10 scale to 0-1 scale

```{r}

all_training_data <-
  all_training_data %>% 
  mutate_at(
    vars(prob, prob_o, like, like_o, imprace, imprelig, sports:exphappy), 
    ~ . / 10
  ) %>% 
  mutate(
    match = as.double(match)
  ) 


cor_data <-
  all_training_data %>% 
  drop_na()

```
## Checking for correlations

```{r, fig.height=20, fig.width=20}

# Convert data to numeric
corr <- 
  cor_data %>% 
  mutate_all(as.integer)

# ggcorr(corr,
#     method = c("pairwise", "spearman"),
#     nbreaks = 6,
#     hjust = 0.8,
#     label = TRUE,
#     label_size = 3,
#     color = "grey50")
```



## Create a train and a validate set

```{r}

random_rows <-
  all_training_data %>%
  pull(rowname) %>% 
  as_tibble %>% 
  sample_frac(0.8) %>% 
  mutate(
    value = as.character(value)
  ) %>% 
  pull(value)

train_model_data <-
  all_training_data %>%
  as_tibble() %>% 
  filter(rowname %in% random_rows)

test_model_data <-
  all_training_data %>%
  anti_join(train_model_data, by = "rowname") %>% 
  select(-rowname) 


lasso_model_data <- 
  train_model_data %>% 
  select(-rowname) %>% 
  mutate_at(vars(condtn), as.factor) %>%
  drop_na()
```

## Using lasso to weed out extraneous vars 

```{r}

# convert the data to a design matrix
X = model.matrix(match ~ 0 + ., lasso_model_data)
Y = lasso_model_data %>% pull(match)


# standardize
X = scale(X)
Y = scale(Y)

set.seed(1244)

# create training and test set
train.ind = sample(nrow(X), round(nrow(X)/2))
X.train = X[train.ind,]
X.test = X[-train.ind,]
Y.train = Y[train.ind]
Y.test = Y[-train.ind]

# set lambda sequence to use for lasso and ridge
lambdas = 10^seq(-2,1.5,0.1)

#lasso
fm.lasso = glmnet(X.train, Y.train, alpha = 1, lambda = lambdas, thresh = 1e-12)

fm.lasso %>%
  summary()

cv <- cv.glmnet(X.train, Y.train)

cv$lambda.min

covars_wanted <-
  extract.coef(cv) %>%
  select(coeff = Coefficient) %>%
  filter(coeff != "(Intercept)") %>%
  pull(coeff)


covars_wanted <-
  covars_wanted %>%
  as_tibble() %>%
  filter(value %in% colnames(train)) %>%
  pull(value)

covars_wanted

# train_model_data <-
#   train_model_data %>% 
#   select(match, all_of(covars_wanted))

```

## Data used

```{r}
# Add in field_cd and career_c b/c rep as factors in covars_wanted
train_model_data <-
  train_model_data %>%
  select(match, attr, sinc, fun, prob, prob_o, like, like_o, avg_partner_rating, imprace, tvsports, clubbing, movies, shopping, age_o)


```

## Functions

### Accuracy

```{r}

accuracy <- function(table_mat) {
  sum(diag(table_mat)) / sum(table_mat)
}


```

### Precision and 
```{r}
precision <- function(matrix) {

    tp <- matrix[2, 2]
	
    fp <- matrix[1, 2]
    return(tp / (tp + fp))
}

recall <- function(matrix) {
    tp <- matrix[2, 2]
    fn <- matrix[2, 1]
    return(tp / (tp + fn))
}

```

## Linear Regression

### With all lasso covariates

```{r}
m1 <-
  glm(
    match ~ ., 
    data = train_model_data, 
    family = 'binomial'
  ) 



predict <- predict(m1, test_model_data, type = 'response')
# confusion matrix
table_mat <- table(test_model_data$match, predict > 0.5)
table_mat

accuracy(table_mat)
precision(table_mat)

recall(table_mat)

```

# ROC curve
```{r}
index <-
  predict[!is.na(predict)] %>% 
  as.data.frame() %>% 
  add_rownames() %>% 
  pull(rowname)


t <-
  test_model_data %>% 
  add_rownames() %>% 
  filter(rowname %in% index)


ROCRpred <- prediction(predict[!is.na(predict)], t$match)
ROCRperf <- performance(ROCRpred, 'tpr', 'fpr')
plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2, 1.7))


```

## Creating a model with interaction terms

```{r}

m2 <-
  glm(
    match ~ . + like:avg_partner_rating + attr:like_o, 
    data = train_model_data, 
    family = 'binomial'
  ) 

m2 %>% 
  summary()



predict <- predict(m2, test_model_data, type = 'response')
# confusion matrix
table_mat <- table(test_model_data$match, predict > 0.5)
table_mat


accuracy(table_mat)
precision(table_mat)

recall(table_mat)


```

```{r}
index <-
  predict[!is.na(predict)] %>% 
  as.data.frame() %>% 
  add_rownames() %>% 
  pull(rowname)


t <-
  test_model_data %>% 
  add_rownames() %>% 
  filter(rowname %in% index)


ROCRpred <- prediction(predict[!is.na(predict)], t$match)
ROCRperf <- performance(ROCRpred, 'tpr', 'fpr')
plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2, 1.7))


```



```{r}

m3 <-
  glm(
    best_formula, 
    train_model_data, 
    family = 'binomial'
  ) 

summary(m3)

```

```{r}

m3 <-
  glm(
    match ~ . + .:., 
    data = train_model_data, 
    family = 'binomial'
  ) 

summary(m3)


predict <- predict(m3, test_model_data, type = 'response')
# confusion matrix
table_mat <- table(test_model_data$match, predict > 0.5)
table_mat

accuracy(table_mat)
precision(table_mat)

recall(table_mat)

x <- 
  summary(m3)

z <-
  x$coefficients %>% 
  as.data.frame() %>% 
  add_rownames() %>% 
  slice(-1) %>% 
  pull(rowname)

formula_wanted <-
  str_c("match ~ ", str_c(z, collapse = " + "))

```

```{r}
index <-
  predict[!is.na(predict)] %>% 
  as.data.frame() %>% 
  add_rownames() %>% 
  pull(rowname)


t <-
  test_model_data %>% 
  add_rownames() %>% 
  filter(rowname %in% index)


ROCRpred <- prediction(predict[!is.na(predict)], t$match)
ROCRperf <- performance(ROCRpred, 'tpr', 'fpr')
plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2, 1.7))


```

## Stepwise AIC regression on model 2

```{r}


train_model_data <-
  train_model_data %>% 
  drop_na()



full_model = glm(match ~ . + .:., family = binomial(), data = train_model_data)

#summary(full_model)


null_model = glm(match ~ 1, family = binomial(), data = train_model_data)

#summary(null_model)

steps <-
  step(null_model, list(upper = full_model), direction = 'forward')


```


```{r}
best_model <-
  glm(formula = match ~ like + like_o + prob + attr + imprace + 
    prob_o + fun + tvsports + avg_partner_rating + clubbing +
    movies + like:prob + like_o:attr + like:avg_partner_rating +
    like:like_o + like_o:prob_o + attr:tvsports + fun:clubbing +
    attr:clubbing + imprace:movies + like:movies + clubbing:movies +
    attr:prob_o + tvsports:clubbing + prob:tvsports + tvsports:avg_partner_rating +
    like:clubbing, family = binomial(), data = train_model_data)

predict <- predict(m2, test_model_data, type = 'response')
# confusion matrix
table_mat <- table(test_model_data$match, predict > 0.5)
table_mat

accuracy(table_mat)
precision(table_mat)
recall(table_mat)


index <-
  predict[!is.na(predict)] %>% 
  as.data.frame() %>% 
  add_rownames() %>% 
  pull(rowname)

summary(best_model)


t <-
  test_model_data %>% 
  add_rownames() %>% 
  filter(rowname %in% index)


ROCRpred <- prediction(predict[!is.na(predict)], t$match)
ROCRperf <- performance(ROCRpred, 'tpr', 'fpr')
plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2, 1.7))

```


