---
title: "Inference on Classification Model"
author: Angela Zhao
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE,dpi=500}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)
library(here)
library(cvTools)
library(coefplot)
library(glmnet)
library(GGally)
library(ROCR)

file_raw_train_data <-
  here("data/train_data_speed_dating.csv")

recode_race <-
  c(
    "1" = "Black", 
    "2" = "White", 
    "3" = "Hispanic", 
    "4" = "API", 
    "5" = "Indigenous",
    "6" = "Other"
  )
  

recode_goal <-
  c(
    "1" = 'Seemed like a fun night out',   
    "2" = "To meet new people",
    "3" = "To get a date", 
    "4" = "Looking for a serious relationship",
    "5" = "To say I did it",
    "6" = "Other"
  )


recode_date <- c(
  "1" = 'Several times a week',   
  "2" = "Twice a week",
  "3" = "Once a week", 
  "4" = "Twice a month",
  "5" = "Once a month",
  "6" = "Several times a year",
  "7" = "Almost never"
)


recode_go_out <-
  c(
    "1" = 'Several times a week',   
    "2" = "Twice a week",
    "3" = "Once a week", 
    "4" = "Twice a month",
    "5" = "Once a month",
    "6" = "Several times a year",
    "7" = "Almost never"
    
  )

```

## Reading and cleaning Data


```{r}
train <-
  file_raw_train_data %>% 
  read_csv()


# Added in the ratings of partner rating you and you rating the partner
# diff is the avg of partner rating you - avg of you rating the partner

train <-
  train %>% 
  mutate_at(
    vars(
      career_c, 
      field_cd,
      race,
      race_o,
      zipcode,
      go_out,
      date,
      goal,
      met,
      met_o,
      samerace,
      gender,
      match
    ), 
    as.character
  ) %>% 
  mutate(
    field_cd = 
      case_when(
        field_cd %in% c("2", "4", "5", "10") ~ "STEM", 
        field_cd %in% c("1", "3", "8", "9", "11", "13") ~ "Social_Science",
        field_cd %in% c("6", "7", "14", "15", "16", "17") ~ "Humanities",
        TRUE ~ "Other"
      ), 
    race = recode(race, !!! recode_race), 
    goal = recode(goal, !!! recode_goal),
    met = if_else(met == "2", "0", met), 
    met_o = if_else(met_o == "2", "0", met_o),
    race_o = recode(race_o, !!! recode_race), 
    gender = if_else(gender == "0", "female", "male"),
    career_c = 
      case_when(
        career_c %in% c("3", "4", "5") ~ "STEM", 
        career_c %in% c("1", "7", "8", "9", "10", "11", "12", "13", "17") ~ "Social_Science",
        career_c %in% c("6") ~ "Humanities",
        TRUE ~ "Other"
      )
  ) %>%
  mutate_at(
    vars(
      career_c,
      field_cd,
      race,
      race_o,
      goal,
      met,
      met_o,
      gender
    ),
    as.factor
  )
```

## Normalize the preferences, if out of 100, to percentages instead. 

```{r}

train <-
  train %>% 
  rowwise() %>% 
  mutate(
    sum_2_1 = sum(c(attr2_1, sinc2_1, intel2_1, fun2_1, amb2_1, shar2_1)), 
    sum_4_1 = sum(c(attr4_1, sinc4_1, intel4_1, fun4_1, amb4_1, shar4_1)),
  ) %>%
  mutate_at(
    vars(attr2_1, sinc2_1, intel2_1, fun2_1, amb2_1, shar2_1), 
    ~ . / sum_2_1
  ) %>%
  mutate_at(
    vars(attr4_1, sinc4_1, intel4_1, fun4_1, amb4_1, shar4_1), 
    ~ . / sum_4_1
  ) %>%
  dplyr::select(-c(sum_2_1, sum_4_1))

train <-
  train %>% 
  rowwise() %>% 
  mutate(
    rating = sum(c(attr, sinc, intel, fun, amb, shar)), 
    avg_partner_rating = 
      mean(c(attr, sinc, intel, fun, amb, shar), na.rm = TRUE) / 10
  ) %>%
  mutate_at(
    vars(attr, sinc, intel, fun, amb, shar), 
    ~ . / rating
  ) %>% 
  select(-rating)

```


## Choosing Variables

```{r}
# Selecting only the variables that determine perception of the round of speed

# Field and career are too unevenly entered, so best to use the coded versions instead. 

vars_wanted <-
  train %>% 
  select(
    rowname, 
    gender, 
    condtn, 
    match:race_o,
    like_o:age, 
    field_cd, 
    race:imprelig, 
    goal:go_out, 
    career_c:exphappy, 
    dec:met, 
    avg_partner_rating
  ) %>%
  select(-c(met, met_o, dec)) %>% 
  summarize_all(~ sum(is.na(.))) %>% 
  summarize_all(~ sum(.)) %>% 
  mutate_all(~ . / 4258) %>% 
  pivot_longer(
    cols = everything(), 
    names_to = "var", 
    values_to = "percent_missing"
  ) %>% 
  filter(percent_missing < 0.5) 

vars_wanted <-
  vars_wanted %>% 
  arrange(desc(percent_missing)) %>% 
  filter(var != "income") %>% 
  pull(var)

all_training_data <-
  train %>% 
  select(rowname, all_of(vars_wanted))


```

## Rescaling 1-10 scale to 0-1 scale

```{r}

all_training_data <-
  all_training_data %>% 
  mutate_at(
    vars(prob, prob_o, like, like_o, imprace, imprelig, sports:exphappy), 
    ~ . / 10
  ) %>% 
  mutate(
    match = as.double(match)
  ) 

```

## Create a test and a validate set

```{r}

lasso_model_data <- 
  all_training_data %>% 
  select(-rowname) %>% 
  mutate_at(vars(condtn), as.factor) %>%
  drop_na()

X <- model.matrix(
  match ~ 0 + ., 
  lasso_model_data, 
  contrasts.arg =
    list(
      goal = contrasts(lasso_model_data$goal, contrasts = F), 
      race = contrasts(lasso_model_data$race, contrasts = F), 
      race_o = contrasts(lasso_model_data$race_o, contrasts = F), 
      gender = contrasts(lasso_model_data$gender, contrasts = F)
    )
)

train_model_data <-
  X %>% 
  as.data.frame() %>% 
  bind_cols(lasso_model_data %>% select(match))

```

## Logistic Regression

```{r}

best_formula <-
  "match ~ attr + sinc + fun + prob + prob_o + like + like_o + avg_partner_rating + imprace + tvsports + clubbing + movies + shopping + age_o + attr:sinc + attr:fun + attr:prob + attr:prob_o + attr:like + attr:like_o + attr:avg_partner_rating + attr:imprace + attr:tvsports + attr:clubbing + attr:movies + attr:shopping + attr:age_o + sinc:fun + sinc:prob + sinc:prob_o + sinc:like + sinc:like_o + sinc:avg_partner_rating + sinc:imprace + sinc:tvsports + sinc:clubbing + sinc:movies + sinc:shopping + sinc:age_o + fun:prob + fun:prob_o + fun:like + fun:like_o + fun:avg_partner_rating + fun:imprace + fun:tvsports + fun:clubbing + fun:movies + fun:shopping + fun:age_o + prob:prob_o + prob:like + prob:like_o + prob:avg_partner_rating + prob:imprace + prob:tvsports + prob:clubbing + prob:movies + prob:shopping + prob:age_o + prob_o:like + prob_o:like_o + prob_o:avg_partner_rating + prob_o:imprace + prob_o:tvsports + prob_o:clubbing + prob_o:movies + prob_o:shopping + prob_o:age_o + like:like_o + like:avg_partner_rating + like:imprace + like:tvsports + like:clubbing + like:movies + like:shopping + like:age_o + like_o:avg_partner_rating + like_o:imprace + like_o:tvsports + like_o:clubbing + like_o:movies + like_o:shopping + like_o:age_o + avg_partner_rating:imprace + avg_partner_rating:tvsports + avg_partner_rating:clubbing + avg_partner_rating:movies + avg_partner_rating:shopping + avg_partner_rating:age_o + imprace:tvsports + imprace:clubbing + imprace:movies + imprace:shopping + imprace:age_o + tvsports:clubbing + tvsports:movies + tvsports:shopping + tvsports:age_o + clubbing:movies + clubbing:shopping + clubbing:age_o + movies:shopping + movies:age_o + shopping:age_o"

 train_model <-
   glm(
    best_formula, 
    data = train_model_data, 
    family = 'binomial'
  ) 


```

## Inference

```{r}

summary(train_model)

predict <- predict(train_model, train_model_data, type = 'response')

table_mat <- table(train_model_data$match, predict > 0.5)
table_mat

accuracy(table_mat)
precision(table_mat)

recall(table_mat)


```

## Bootstrapping

```{r}

n <- nrow(train_model_data)

rep <- 1000

coef_data <-
  train_model$coefficients %>% 
  as.list() %>% 
  as_tibble %>% 
  select(-"(Intercept)") %>% 
  pivot_longer(
    cols = everything(), 
    names_to = "coef", 
    values_to = "val"
  ) %>% 
  select(-val)

  

for (i in 1:rep) {
  data <-
    train_model_data %>% 
    slice_sample(n = n, replace = TRUE)
  
  model <-
    glm(
      best_formula, 
      data = data, 
      family = 'binomial'
    ) 
  
  model_coef <-
    model$coefficients %>% 
    as.list() %>% 
    as_tibble %>% 
    select(-"(Intercept)") %>% 
    pivot_longer(
      cols = everything(), 
      names_to = "coef", 
      values_to = str_c("val_", as.character(i))
    )
  
  coef_data <-
    coef_data %>% 
    left_join(
      model_coef, 
      by = "coef"
    )
  
}

```

### Calculating confidence intervals

```{r}

coef_se <-
  as_tibble(cbind(nms = names(coef_data), t(coef_data))) %>% 
  janitor::row_to_names(row_number = 1) %>% 
  rename(
    rep = coef
  ) %>% 
  select(-rep) %>% 
  summarise(across(everything(), sd)) %>%
  pivot_longer(
    cols = everything(), 
    names_to = "coef", 
    values_to = "se"
  )

coef_ci <-
  coef_data %>% 
  mutate(
    mean = rowMeans(select(., starts_with("val")), na.rm = TRUE)
  ) %>% 
  select(coef, mean) %>% 
  left_join(
    coef_se, 
    by = "coef"
  )

coef_ci


```

## Looking at distribution of coefficients

All are relatively normal, so we can use SE to estimate the confidence intervals 
```{r}

coef_distr <-
  as_tibble(cbind(nms = names(coef_data), t(coef_data))) %>% 
  janitor::row_to_names(row_number = 1) %>% 
  rename(
    rep = coef
  ) %>%
  mutate_at(vars(-rep), as.double) %>% 
  select(-rep) %>% 
  rename_all(~ str_remove_all(., ":"))

hist_func <- function(var) {
  coef_distr %>% 
  ggplot(aes_string({{var}})) +
  geom_histogram()
}


vars <-
  coef_distr %>% 
  colnames() 

vars %>% 
  map(~ hist_func(.))

```

## Estimating confidence intervals

```{r}
coef_ci %>%
  mutate(
    lower_95 = mean - 1.96*se, 
    upper_95 = mean + 1.96 * se, 
    sig = 
      if_else(
        lower_95 > 0 | upper_95 < 0, 
        TRUE, 
        FALSE
      )
  ) %>% 
  filter(sig)


training_r_sig <-
  c("imprace", "fun:avg_partner_rating", "fun:clubbing", "fun:movies", "tvsports:shopping")

coef_ci %>% 
  as_tibble() %>% 
  mutate(
    lower_95 = mean - 1.96*se, 
    upper_95 = mean + 1.96 * se, 
    sig = 
      if_else(
        lower_95 > 0 | upper_95 < 0, 
        TRUE, 
        FALSE
      )
  ) %>%
  filter(coef %in% training_r_sig)

```
```{r}
all <-
   glm(
    match ~ . + .:., 
    data = train_model_data, 
    family = 'binomial'
  ) 


summary(all)
```

